A large scale grammar and parser for Swedish

### 2011-11-15 doc/report/report.tex
documentation and report

\subsection{Mapping}
To connect GF with other annotations, to evaluate. Identify missing constructs,
missing words. More reasons from presentation.
Similar for English and Penntree, but PennTree and Talbanken different, plus swedish
makes a different. More possible word orders (or at least more commonly used).
How we try to build up a 'parse tree', a S with a NP VP for example. 
How verbs look for complements (or inverted order), how metas are added.
Description of most important tags from Talbanken, their translation.
Description of the ones most hard to translate (particles, flat sentences)
Example of nice translation and one with many metas, and one that doesn't work.
Developed by adding one mapping for each tag, and by examples.
How we cannot cover all cases. The testing: regression testing again,
very easy to destroy what was working before. 
How we need valency information.
Evaluation.

@@

Grammar - hard to evaluate automatically, but Elibet is an expert who has been involved
in the process to verify the solutions. Testing trees against talbanken.

>>>>

\subsection{Mapping}
To connect GF with other annotations, to evaluate. Identify missing constructs,
missing words. More reasons from presentation.
Similar for English and Penntree, but PennTree and Talbanken different, plus swedish
makes a different. More possible word orders (or at least more commonly used).
One deep and one flatter version of Talbanken, deep contains ca 5 more tags.
The flat was used since the deep one
isn't deep in the same way as GF. Example with CNP (s5). Some
more info about VPs are given, but do not think this will give any relevant information.
Talbanken also contains frequent .. tags XP, XX osv. We cannot expect to translate
this to anything but metas.
How we try to build up a 'parse tree', a S with a NP VP for example. 
How verbs look for complements (or inverted order), how metas are added.
Description of most important tags from Talbanken, their translation.
Description of the ones most hard to translate (particles, flat sentences)
Example of nice translation and one with many metas, and one that doesn't work.
Developed by adding one mapping for each tag, and by examples.
How we cannot cover all cases. The testing: regression testing again,
very easy to destroy what was working before. 
How we need valency information.
If we don't take the verb valency into account, allow all verbs to have Gf category V,
we get a slightly better result,
from 62.5\% to 65.4\%.  (see EvalText). The complemnt of the verbs should tell which category
they are anyway.
Evaluation.

@@

Grammar - hard to evaluate automatically, but Elibet is an expert who has been involved
in the process to verify the solutions. Testing trees against talbanken.
The big lexicon makes it very slow, eats all memory
